---
title: "User-Defined Cross-Section Application"
author: "Muhammad Malik Ar Rahiem"
date: "3/24/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
library(mapedit)
library(leaflet)
library(mapview)
library(tidyverse)
library(sf)

url <- "https://raw.githubusercontent.com/malikarrahiem/thesismalik/master/Complete_Logs.csv?token=AMDKGMXFOOP6CAQ4JJ2OJXS6ODU6A"
Logs <- read.csv(url, header = TRUE)

Warna <- c("Andesit" = "red4", "TanahPenutup" = "peru", 
           "Tufa" = "darkorange", "Pasir" = "yellow2", 
           "Lempung" = "forestgreen", "Screen" = "blue",
           "Breksi" = "chocolate4", "Kerikil" = "yellow",
           "Lava" = "red1")

url <- "https://raw.githubusercontent.com/malikarrahiem/thesismalik/master/Complete_Logs.csv?token=AMDKGMXFOOP6CAQ4JJ2OJXS6ODU6A"
Logs <- read.csv(url, header = TRUE)

datamap <- selectMap(
  leaflet(Logs) %>%
    addTiles() %>%
    addCircleMarkers(data = Logs, 
                                      ~Longitude, ~Latitude, 
                                      layerId = ~KodeSumur, 
                                      popup = ~KodeSumur, 
                                      radius = 5, 
                                      weight= 5,
                                      stroke = TRUE,
                                      label = ~KodeSumur,
                                      color = 'navy',
                                      group = "Wells")
)

datamap

```

## User Defined Cross Section Application

This is the function that is not yet available in the apps due to the incompatibility between the packages behind this function. The function can be used to plot a well cross section that pass through any points that are selected by user. User can select any points, afterward save it and shows it as a cross section. Similar to the function of Predefined Well Cross-Section, but in this case, the points are user-defined. 

```{r User-Defined Cross Section, echo=}

PlotGrafik <- function(x){
  WS <- x %>% 
    dplyr::select(KodeSumur, TopElev, BotElev, Screen) %>% 
    filter(Screen == "Screen")
  
  if(dim(WS)[1] == 0) {
    ggplot()+
      geom_rect(data = x,
                mapping = aes(xmin=BotElev, xmax=TopElev, 
                              ymin=0, ymax= 50,
                              colour="grey",
                              weight = 0.2,
                              fill=NA))+
      scale_color_manual(values=c('grey'),
                         guide=FALSE)+
      geom_rect(data = x, 
                mapping = aes(xmin=BotElev, xmax=TopElev, 
                              ymin=0, ymax= 50, fill= KodeLito))+
      facet_wrap(~KodeSumur, ncol = 10)+
      geom_line(data= x, mapping = aes(x= TopElev, y= R))+
      theme_bw()+ 
      coord_flip()+
      scale_y_continuous(, limits=c(-10,150))+
      scale_fill_manual(values = Warna)+
      labs(x = "Elevation (masl)" , y = "Resistivity (Ohm.m)", fill = "Legend")+
      theme(legend.position = "bottom")+
      guides(fill = guide_legend(nrow = 1))
    
  } else {
    ggplot()+
      geom_rect(data = x,
                mapping = aes(xmin=BotElev, xmax=TopElev, 
                              ymin=0, ymax= 50,
                              colour="grey",
                              weight = 0.2,
                              fill=NA))+
      scale_color_manual(values=c('grey'),
                         guide=FALSE)+
      geom_rect(data = WS, 
                mapping = aes(xmin=BotElev, xmax=TopElev, 
                              ymin=-5, ymax= 55, fill= Screen))+
      geom_rect(data = x, 
                mapping = aes(xmin=BotElev, xmax=TopElev, 
                              ymin=0, ymax= 50, fill= KodeLito))+
      facet_wrap(~KodeSumur, ncol = 10)+
      geom_line(data= x, mapping = aes(x= TopElev, y= R))+
      theme_bw()+ 
      coord_flip()+
      scale_y_continuous(, limits=c(-10,150))+
      scale_fill_manual(values = Warna)+
      labs(x = "Elevation (masl)" , y = "Resistivity (Ohm.m)", fill = "Legend")+
      theme(legend.position = "bottom")+
      guides(fill = guide_legend(nrow = 1))
  }
}

PlotPenampang <- function (x){
  KodeSumur2 <- datamap$id
  x <- Logs[Logs$KodeSumur %in% KodeSumur2,] %>% 
    mutate(KodeSumur=factor(KodeSumur, levels = datamap$id)) %>% 
    arrange(KodeSumur)
  PlotGrafik(x)
}

PlotPenampang(datamap)
```
